Scottish Child Payment Interventions

### 2024-01-18 minos/outcomes/SCP_vis.Rmd
More additions to SCP plotting scripts, added some decile plots

#int.list <- c(int25, int30, int35, int40, int45, int50)
int.list <- list(base, int25, int30, int35, int40, int45, int50)
# 
scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')

@@

```{r}
# single.mean <- function(data, scen) {
#   newvar.name <- paste0(scen, '.SF12')
#   print(newvar.name)
#   data <- data %>%
#     select(time, weight, SF_12) %>%
#     group_by(time) %>%
#     summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
#   return(data)
# }
# 
# int.list <- list(base, int25, int30)
# 
# scen.list <- c('base', 'int25', 'int30')
# 
# #mod.list <- lapply(int.list, single.mean, scen.list)
# #mod.list <- mapply(single.mean, int.list, scen.list)
# 
# mod.list <- mapply(single.mean, int.list, scen.list, SIMPLIFY = FALSE)
# 
# combined <- mod.list %>%
#   reduce(full_join, by='time')
# 
# # List of intervention columns
# int_cols <- grep("int\\d+.SF12", names(combined), value = TRUE)
# 
# # # Create the new dataframe with differences
# # combined_diff <- combined %>%
# #   mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}"))
# 
# # Create the new dataframe with differences
# combined_diff <- combined %>%
#   mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
#   select(time, starts_with("diff")) %>%
#   rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))

@@

@@

>>>>

#int.list <- c(int25, int30, int35, int40, int45, int50)
int.list <- list(base, int25, int30, int35, int40, int45, int50)
scen.list <- c('base', 'int25', 'int30', 'int35', 'int40', 'int45', 'int50')

@@

@@

```{r SF12_deciles, echo=FALSE}
SF12.by.simd.deciles <- function(df.list, scen.list, start.year = 2020, batch=FALSE) {
  single.mean <- function(data, scen, start.year) {
    newvar.name <- paste0(scen, '.SF12')
    data <- data %>%
      select(time, weight, simd_decile, SF_12) %>%
      filter(time >= start.year) %>%
      group_by(time, simd_decile) %>%
      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
    return(data)
  }
  batch.mean <- function(data, scen, start.year) {
    newvar.name <- paste0(scen, '.SF12')
    data <- data %>%
      select(time, weight, simd_decile, run_id, SF_12) %>%
      filter(time >= start.year) %>%
      group_by(time, run_id) %>%
      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
    return(data)
  }

  if (batch) {
    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
    combined <- mod.list %>%
      reduce(full_join, by=c('time', 'simd_decile', 'run_id'))
  } else {
    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
    combined <- mod.list %>%
      reduce(full_join, by=c('time', 'simd_decile'))
  }

  combined$simd_decile <- as.factor(combined$simd_decile)

  int.labels <- scen.list[-1]

  for (int in int.labels) {
    int.name <- paste0(int, '.SF12')
    if (batch) {
      p1 <- ggplot(combined, aes(x = time, group = simd_decile, colour = simd_decile)) +
        geom_smooth(aes(y = base.SF12)) +
        geom_smooth(aes(y = .data[[int.name]]), linetype='dashed') +
        labs(title = 'SF12 MCS Deciles', subtitle = paste0('Baseline vs ', int)) +
        xlab('Year') +
        ylab('Difference')
    } else {
      p1 <- ggplot(combined, aes(x = time, group = simd_decile, colour = simd_decile)) +
        geom_line(aes(y = base.SF12)) +
        geom_line(aes(y = .data[[int.name]]), linetype='dashed') +
        labs(title = 'SF12 MCS Deciles', subtitle = int) +
        xlab('Year') +
        ylab('Difference')
    }
    print(p1)
  }
}
```

```{r SF_change_deciles, echo=FALSE}
SF12.change.by.deciles <- function(df.list, scen.list, start.year = 2020, batch = FALSE) {
  single.mean <- function(data, scen, start.year) {
    newvar.name <- paste0(scen, '.SF12')
    data <- data %>%
      select(time, weight, simd_decile, SF_12) %>%
      filter(time >= start.year) %>%
      group_by(time, simd_decile) %>%
      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
    return(data)
  }
  batch.mean <- function(data, scen, start.year) {
    newvar.name <- paste0(scen, '.SF12')
    data <- data %>%
      select(time, weight, simd_decile, run_id, SF_12) %>%
      filter(time >= start.year) %>%
      group_by(time, run_id) %>%
      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
    return(data)
  }

  if (batch) {
    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
    combined <- mod.list %>%
      reduce(full_join, by=c('time', 'simd_decile', 'run_id'))
  } else {
    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
    combined <- mod.list %>%
      reduce(full_join, by=c('time', 'simd_decile'))
  }

  combined$simd_decile <- as.factor(combined$simd_decile)

  # Create the new dataframe with differences
  combined <- combined %>%
    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
    select(time, simd_decile, starts_with("diff")) %>%
    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))

  options(repr.plot.width =9, repr.plot.height =20)

  p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype='dashed') +
    facet_wrap(. ~ scen, ncol=1) +
    labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
    xlab('Year') +
    ylab('Difference')

  ggsave(filename = 'test_plot.png',
         plot = p1,
         path = here::here('plots', 'SCOTGOVWORK'),
         width = 9,
         height = 20)

@@

## MCS - DECILES

```{r}
SF12.by.simd.deciles(int.list, scen.list)
```

```{r}
SF12.by.simd.deciles(int.list, scen.list, start.year = 2024, batch = FALSE)
```

## MCS - CHANGE BY DECILES

```{r}
SF12.change.by.deciles(int.list, scen.list)
```

## TESTING

```{r}
```
